---
title: "Case Study 2"
author: "Michael Daniel Bigler and Liam Arthur Phan"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    code_folding: hide
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	fig.align = "center")
rm(list = ls())
cat("\014")

```

<break>

> Goal:

# Packages

> In the following all the packages needed for this case study are loaded.

```{r packages}

library(ggplot2)
library(DT)
library(jtools)
library(kableExtra)
library(pastecs)

```

# Data

> . The source is thereby listed below.

> Source: **Advanced Data Driven Decision Making** [S401024](https://moodle.unige.ch/course/view.php?id=2675 "2675") - University of Geneva (GSEM)
>
> Marcel Paulssen, Professor\
> Fereshteh Vahidi, Teaching Assistant\
> Anastasia Floru, Teaching Assistant

```{r data loading}
Mydata <- read.csv("DATA/Data File_Case_Study_Factor Analysis_MD.csv", header=TRUE)

# selecting questions
Mydata_with_y <- Mydata[,c(9:41, 43:45, 51:52)]
Mydata_qd <- Mydata[,9:41]
```

## Data Analysis

```{r}
list_na =colnames(Mydata_with_y)[apply(Mydata_with_y,2,anyNA)]
list_na
```

There are missing values

```{r}
stat.desc(Mydata_with_y, norm=TRUE)
```

# Orthogonal Factor Analysis

# Oblique Factor Analysis
